Malacology: A Programmable Storage System

### 2016-10-17 paper/paper.tex
tweaks

Building storage stacks from the ground-up for a specific purpose results in
the best performance. For example, HDFS was designed specifically to serve
Hadoop's jobs~\paa{lol not sure if I buy that hadoop achieves ``best performance''}, and uses techniques like exposing data locality and relaxing POSIX constraints to achieve
the best performance~\cite{CITEME}. Alternatively, general-purpose storage
stacks are built with the flexiblity to serve many applications by providing a
variety of interfaces and tunable parameters. Unfortunately, managing competing
forces in these systems is difficult and users
want more control from the general-purpose storage stacks
without going as far as building their storage system from the ground up.

@@

To demonstrate this trend in storage systems we examine the state of
programmability in Ceph. Something of a storage swiss army knife, Ceph simultaneously supports file,
block, and object interfaces on a single
cluster~\cite{ceph_contributors_ceph_2010}. Ceph's Reliable Autonomous
Distributed Object Storage (RADOS) system is a cluster of storage devices
(OSDs) that provide Ceph with data durability and integrity using replication,
erasure-coding, and scrubbing~\cite{weil_rados_2007}. Ceph already has some
programmability; the OSDs support domain-specific object interfaces that are
implemented by composing existing low-level storage interfaces that execute
atomically. These interfaces are
written in C++ and are statically loaded into the system.

@@

The Ceph community provides empirical evidence that developers embrace
programmable storage. Figure~\ref{fig:obj-int-dev-growth} shows a dramatic
growth in the production use of domain-specific interfaces in the Ceph
community since 2010. In that figure, classes are functional groupings of methods on storage
objects.  What is most remarkable is that this trend contradicts the notion
that API changes are a burden for users.  Rather it appears that a gap in
existing interfaces are being addressed through programmability. In fact,
Table~\ref{table:objclasses} categorizes existing interfaces and we clearly see
a trend towards reusable services.

>>>>

Building storage stacks from the ground up for a specific purpose results in
the best performance. For example, HDFS was designed specifically to serve
Hadoop's jobs~\paa{lol not sure if I buy that hadoop achieves ``best performance''}, and uses techniques like exposing data locality and relaxing POSIX constraints to achieve
the best performance~\cite{CITEME}. Alternatively, general-purpose storage
stacks are built with the flexiblity to serve many applications by providing a
variety of interfaces and tunable parameters. Unfortunately, managing competing
forces in these systems is difficult and users
want more control from the general-purpose storage stacks
without going as far as building their storage system from the ground up.

@@

To demonstrate this trend in storage systems we examine the state of
programmability in Ceph. Something of a storage swiss army knife, Ceph simultaneously supports file,
block, and object interfaces on a single
cluster~\cite{ceph_contributors_ceph_2010}. Ceph's Reliable Autonomous
Distributed Object Storage (RADOS) system is a cluster of storage devices
(OSDs) that provide Ceph with data durability and integrity using replication,
erasure-coding, and scrubbing~\cite{weil_rados_2007}. Ceph already 
%has some
provides some degree of
programmability; the OSDs support domain-specific object interfaces that are
implemented by composing existing low-level storage interfaces that execute
atomically. These interfaces are
written in C++ and are statically loaded into the system.

@@

The Ceph community provides empirical evidence that developers are already beginning to embrace
programmable storage. Figure~\ref{fig:obj-int-dev-growth} shows a dramatic
growth in the production use of domain-specific interfaces in the Ceph
community since 2010. In that figure, classes are functional groupings of methods on storage
objects.  What is most remarkable is that this trend contradicts the notion
that API changes are a burden for users.  Rather it appears that a gap in
existing interfaces are being addressed through ad-hoc approaches to programmability. In fact,
Table~\ref{table:objclasses} categorizes existing interfaces and we clearly see
a trend towards reusable services.
